Adaptive Scheduling of Scientific Workflows

### 2024-03-10 main.tex
More related work

    Daniels et al.

@@

>>>>

    Daniels et al.~\cite{daniels1995robust} formalize the concept of robust scheduling with variable processing times
    on a single machine.
    The changes in runtimes of tasks are not due to changing machine properties, but are rather task-related (that means
    that these runtime changes are unrelated to each other).
    The authors formulate a decision space of all permutations of n jobs, and the optimal schedule in relation to a
    performance measure $\phi$.
    Then they proceed to formulate the Absolute Deviation Robust Scheduling Problem as a set of linear constraints.

@@

    Garg~\etal~\cite{GARG2015256} propose a dynamic scheduling algorithm for heterogeneous grids based on rescheduling.
    The aim is to minimize the makespan, and the experiments were conducted on a single wotkflow with 10 tasks.
    The procesdure involves building a first (static) schedule, priodic resource monitoring and rescheduling the remaining
    tasks.
    The resource model contains resource groups (small tightly-connected sub-clusters), connected between each other.
    For each resuorce group, there is an own scheduler, and an overall global scheduler responsible for distributing
    tasks to groups.
    The authors define the execution time, estimated start time, data ready time,a dn estimated finish time per task.
    The runtimes of tasks depend on processor speeds, are calculated in advance and stored in tables.

    The algorithm first computes bottom levels for all tasks (execution time is average of all possible execution times).
    THe bottom level represents the priority of the task, and tasks are sorted according to these priorities.
    They then go through tasks and map than to such processors that minimize the earliest start times of this task's
    successors.
    To do this, the authors calculate the earliest finishing time of the task across all ressources, along with the
    average communication and computation costs fir the dependent tasks.

    The rescheduling is being triggered when either a load on a resource increases over a threshold, or if a new resource
    is added.
    The algorithm produces a new mapping from scrath, and this mapping is being accepted if the resulting maespan is
    smaller than the previously predicted one.
